\section{Imitation}

In this test we evaluate the ability of a robot to learn from human performance
and therefore also advanced manipulation of objects like picking and placing as 
well as advanced interaction between objects like pouring. The robot should 
reason about what a person is doing with the objects it is interacting.

For this task we expect all robot behaviours from Category 1 and Category 2 of
the GPSR test. A person is executing a task, the robot should classify it by observation
and be able to execute it afterwards by translating it into known behaviours that
are performed during Stage 1 tests. Some manipulation actions also need to be
added according to the limited set of actions of Stage 1.

For that the robots needs to solve human-object relations and classify an action
based on the observation.

The task will be divided as follows:

\begin{itemize}
	\item Initial Scene Observation
	\item Action Observation
	\item Action Execution
\end{itemize}


\subsection{Focus}
This test particularly focuses on the following aspects:
\begin{itemize}
	\item No predefined order of actions to carry out.
	\item Action analysis and understanding.
	\item Increased complexity and focus on action recognition and manipulation (unlike GPSR where focus is on speech recognition and speech understanding).
	\item Environmental (high-level) reasoning.
	\item Task execution.
\end{itemize}

\subsection{Task}

\begin{enumerate}
\item \textbf{Entering:} The robot enters the apartment to a predefined location 
	and is positioned on the opposite site of a human demonstrator. After entering 
	the robot could execute an initial scene analysis. All objects that are used 
	during the performance are already placed on the table.

	\item \textbf{Action observation:} The operator starts the learning phase 
		by voice "Watch me now". The person then interacts with the objects. Potential
		actions can be: \\
		\begin{itemize}
			\item Picking
			\item Placing
			\item Pouring
			\item Stacking
			\item ...
		\end{itemize}

	\item \textbf{Action classification:} The robot should announce by voice it just analysed
		from the performance. Each task contains a sequence of three basic actions.

	\item \textbf{Action execution:} Then the robot is triggered by voice "Perform what you just saw"
		and tries to repeat the observed action. (The initial state will be recreated then (in terms of that 
		the same objects are on the table, positions and order can vary.)

\end{enumerate}

\subsection{Additional rules and remarks}
\label{sec:imitation_remarks}
\begin{enumerate}
	\item \textbf{Referees:} Since the score system in this test involves a 
		subjective evaluation of the robot's behavior, the referees are EC/TC members.

	\item \textbf{Operator:} The person operating the robot is one of the 
		referees (default operator).

	\item \textbf{Incremental scoring:} Scores will be awarded for the correct
		announcement of the classified action including the interacting objects.
		The actual execution of the correctly associated sequence of actions 
		will be awarded. Each correct sub-action will be taken into account.
\end{enumerate}

\subsection{Referee and OC instructions}
\textbf{2h before test:}
\begin{itemize}
	\item Specify objects, possible object affordances
	\item initial location.
\end{itemize}

\newpage
\subsection{Score sheet}

%TODO (Raphael): Scoresheet
%\input{scoresheets/imitation.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:
